Titeln på avhandlingens språk

### 2023-05-11 body/acks.tex
acks

Furthermore, I would like to extend my sincere thanks to Prof. Sandra Céspedes, of Universidad de Chile and Concordia University, for her guidance and urging to embark on this journey towards a Ph.D., and for always being willing to offer help and advice.
Likewise, I'd like to thank Prof. Javier Bustos, of Universidad de Chile and NIC Chile Research Labs, for giving me the opportunity many years ago to first get into distributed systems research.
Also, I'd like to extend my gratitude to Prof. José Miguel Piquer, of Universidad de Chile, for taking me as his ``long-distance'' teaching assistant and allowing me to give back to my \emph{alma mater} from across the ocean.
A very special thanks goes out to Prof. Jérémy Barbay of Universidad de Chile and Universidad de Concepción, for being a mentor and a friend since the day I took his course on Android programming while an undergraduate student.
I am deeply appreciative of the fact that although our interactions have been sporadic at best these last few years, I can always reach out to him for help and advice when I need it.

>>>>

Furthermore, I would like to extend my sincere thanks to Prof. Sandra Céspedes, of Universidad de Chile and Concordia University, for her guidance and urging to embark on this journey towards a Ph.D., and for always being willing to offer help and advice.
Likewise, I'd like to thank Prof. Javier Bustos, of Universidad de Chile and NIC Chile Research Labs, for giving me the opportunity many years ago to first get into distributed systems research.
Also, I'd like to extend my gratitude to Prof. José Miguel Piquer, of Universidad de Chile, for taking me as his ``long-distance'' teaching assistant and allowing me to give back to my \emph{alma mater} from across the ocean.
A very special thanks goes out to Prof. Jérémy Barbay of Universidad de Chile and Universidad de Concepción, for being both a mentor and a friend since the day I took his course on Android programming as an undergraduate student.
I am deeply appreciative of the fact that although our interactions these last few years have been sporadic at best, I can always reach out to him for help and advice when I need them.
